---
title: "SAT Active Risk Report"
output:
  word_document:
    reference_docx: ref_format.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(tidyverse)
library(Rblpapi)
library(pbapply)
library(lubridate)
library(RcppRoll)
library(scales)
library(knitr)

blpConnect()

# Read in details of instruments, including matching their codes to the Bloomberg tickers
# govt <- read.csv("inputs/tickers_govt_clean.csv", stringsAsFactors = FALSE)
# ilb <- read.csv("inputs/tickers_ilb_clean.csv", stringsAsFactors = FALSE)
# bonds <- bind_rows(govt, ilb) %>%
#   mutate(country = as.factor(country),
#          maturity = as.factor(country),
#          type = as.factor(type),
#          asset =as.factor(asset))
# futures <- read.csv("inputs/tickers_futures.csv", stringsAsFactors = FALSE) %>%
#   mutate(original_ticker = ticker,
#          ticker = str_replace(original_ticker, "(?i) comdty", " B:00_0_D Comdty")) # Roll differencing, see ‘DOCS #2072138 <GO> on Bloomberg
# equity <- read.csv("inputs/tickers_equity.csv", stringsAsFactors = FALSE)
# fx_funding <- read.csv("inputs/tickers_funding.csv", stringsAsFactors = FALSE)
# 
# others <- read.csv("inputs/tickers_others.csv", stringsAsFactors = FALSE)
# 
# cds <- others %>% filter(asset == "cds") 
```

```{r rebuild}
strategies_list <- build_strategies("../data2/strategies.csv")
instr_df <- strategies_list$summary
portfolios_list <- strategies_list[names(strategies_list) != "summary"]

dur_df <- get_dur_bbg(instr_df)
clean_pf_list <- map(portfolios_list, 
                  ~convert_dur_size(., instr_df, dur_df))

asset_returns <- get_ret_bbg(instr_df)
wt_returns <- map(clean_pf_list, 
                  ~calc_strat_wt_return(., asset_returns))

strat_headline_size <- map(clean_pf_list, 
                           ~calc_strat_headline_size(.))

unwt_returns <- map2(wt_returns, strat_headline_size, calc_strat_unwt_return)

active_risk <- calc_active_risk(unwt_returns$sim, 
                                get_strat_size(strat_headline_size$actual, as.Date("2018-11-28")),
                                start_date = as.Date("2017-11-28"), end_date = as.Date("2018-11-28"))

```


```{r get_strategies}
dir()
# Read in strategies 
strategy_file <- "../data2/strategies.csv"
strategies <- read.csv(strategy_file, stringsAsFactors = FALSE) %>%
  mutate(open_date = ymd(open_date), close_date = ymd(close_date),
         asset_class = as.factor(asset_class),
         size_type = as.factor(size_type),
         strategy = paste(strategy, owner, sep = ":::"))

# Filter out strategies which are still open, indicated by the lack of a close date
active_strategies <- strategies %>%
  filter(is.na(close_date)) %>%
  arrange(desc(owner)) %>%
  .$strategy %>%
  unique %>%
  rev

## Check that all instruments' tickers are known

# Check asset classes
valid_asset_class <- c("govt", "ilb", "future", "equity", "cds", "fx")
asset_classes <- unique(strategies$asset_class)
                      
if (mean(asset_classes %in% valid_asset_class) < 1)
  stop(paste("Invalid asset class found in", strategy_file, ":", paste(asset_classes[! asset_classes %in% valid_asset_class], collapse = ",")))

# Check bonds
strat_bond <- strategies %>% filter(asset_class == "govt" | asset_class == "ilb") %>% .$instrument

if (mean(strat_bond %in% bonds$identifier) < 1) 
  stop(paste("Bond identifier unknown in", strategy_file, ":", paste(strat_bond[! strat_bond %in% bonds$identifier], collapse = ",")))

# Check futures
strat_future <- strategies %>% filter(asset_class == "future") %>% .$instrument

if (mean(strat_future %in% futures$identifier) < 1) 
  stop(paste("Future identifier unknown in", strategy_file, ":", paste(strat_future[! strat_future %in% futures$identifier], collapse = ",")))

# Check equity indices
strat_equity <- strategies %>% filter(asset_class == "equity") %>% .$instrument

if (mean(strat_equity %in% equity$identifier) < 1) 
  stop(paste("Equity identifier unknown in", strategy_file, ":", paste(strat_equity[! strat_equity %in% equity$identifier], collapse = ",")))

# Check CDS indices
strat_cds <- strategies %>% filter(asset_class == "cds") %>% .$instrument

if (length(strat_cds) > 0 && mean(strat_cds %in% cds$identifier) < 1) 
  stop(paste("Equity identifier unknown in", strategy_file, ":", paste(strat_cds[! strat_cds %in% cds$identifier], collapse = ",")))

# Check FX
strat_fx <- strategies %>% filter(asset_class == "fx") %>% .$instrument

if (mean(nchar(strat_fx) == 6) < 1)  # FX errors identified by ticker being not equal to 6 characters
  stop(paste("FX identifier unknown in", strategy_file, ":", paste(strat_fx[nchar(strat_fx) != 6], collapse = ",")))

```

```{r get_duration, message = FALSE, echo = FALSE, warning = FALSE}
# Get tickers for duration

## Bond instruments
uniq_inst_bonds <- data.frame(instrument = unique(filter(strategies, size_type == "months" & asset_class != "future")$instrument), 
                              stringsAsFactors = FALSE) %>%
  left_join(select(bonds, identifier, ticker), by = c("instrument"="identifier")) %>%
  transmute(name = instrument, 
            ticker = ticker)

## Future instruments
uniq_inst_fut <- data.frame(instrument = unique(filter(strategies, size_type == "months" & asset_class == "future")$instrument), 
                            stringsAsFactors = FALSE) %>%
  left_join(select(futures, identifier, ticker), by = c("instrument"="identifier")) %>%
  transmute(name = instrument, 
            ticker = ticker)

## CDS instruments
uniq_inst_cds <- data.frame(instrument = unique(filter(strategies, size_type == "months" & asset_class == "cds")$instrument), 
                            stringsAsFactors = FALSE) %>%
  left_join(select(cds, identifier, ticker_duration, ticker_return), by = c("instrument"="identifier")) %>%
  mutate(name = instrument, 
            ticker = ticker_duration)

# Download durations for bonds
bond_dur <- bdh_batch(uniq_inst_bonds, "MODIFIED_DURATION")
all_dur <- bond_dur

# Download duration for futures
if (nrow(uniq_inst_fut) > 0) {
  fut_dur <- bdh_batch(uniq_inst_fut, "FUT_EQV_DUR_NOTL")
  
  # Some futures such as Euribor futures does not have historical duration, 
  #  hence we need to use the most recent duration and apply it to the history
  recent_dur <- bdp(uniq_inst_fut$ticker, "FUT_EQV_DUR_NOTL")
  for (i in 2:ncol(fut_dur)) {
    curr_sec <- names(fut_dur)[i]
    curr_ticker <- uniq_inst_fut$ticker[uniq_inst_fut$name == curr_sec]
    if (mean(is.na(fut_dur[,i])) == 1) {  # If all duration from the historical series is NA
      fut_dur[,i] <- recent_dur[rownames(recent_dur) == curr_ticker,]   # we replace with the most recent duration
    }
  }
  # Combine futures and bond duration
  all_dur <- left_join(fut_dur, bond_dur, by="date")
  
}

# Download spread duration for CDS
if (nrow(uniq_inst_cds) > 0) {
  cds_dv01 <- bdp(uniq_inst_cds$ticker, "SW_EQV_BPV") 
  
  cds_dur <- abs(cds_dv01 * 10000 / 1e7) %>%
    rownames_to_column("ticker") %>%
    left_join(uniq_inst_cds, by = "ticker")
  
  # Combine spread duration of CDS with other durations
  for (i in 1:nrow(cds_dur)) {
    all_dur[cds_dur$instrument[i]] <- cds_dur$SW_EQV_BPV[i]
  }
}

# Some instruments have very short duration history e.g. ILBs, hence we just assume all previous to be the first duration. 
all_dur <- tidyr::fill(all_dur, everything(), .direction = "up")

# Create blank placeholder dataframe with dates, to use later to harmonize dates
blank_df <- select(all_dur, date) 

all_dur_no_date <- remove_date(all_dur)
```

```{r get_returns, message = FALSE, echo = FALSE, warning = FALSE}
###############################################
# DOWNLOAD RETURN DATA DATA FOR ALL ASSETS
###############################################

# GOVT, ILB, EQUITY, FUTURES: select those only required by the strategies

## GOVT AND ILB
filtered_bonds <- bonds %>% filter(identifier %in% strategies$instrument) %>%
  transmute(name = identifier,
         ticker = ticker) 

## EQUITY
filtered_equity <- equity %>% filter(identifier %in% strategies$instrument) %>%
  transmute(name = identifier,
         ticker = ticker)

## FUTURES
filtered_futures <- futures %>% filter(identifier %in% strategies$instrument) %>%
  transmute(name = identifier,
            ticker = ticker)

## CDS
filtered_cds <- cds %>% filter(identifier %in% strategies$instrument) %>%
  mutate(name = identifier,
         ticker =ticker_return)

### Download return index for bonds and equity from BBG
ret_index <- bdh_batch(rbind(filtered_bonds, filtered_equity))

# Download futures price if there are any futures traded
if (nrow(filtered_futures) > 0) { 
  ret_index_2 <- bdh_batch(filtered_futures, "CONTRACT_VALUE")
  ret_index <- merge(ret_index, ret_index_2, by = "date")
}

# Download CDS prices if CDS is used
if (nrow(filtered_cds) > 0) {
  cds_ret_index <- bdh_batch(filtered_cds)
  ret_index <- merge(ret_index, cds_ret_index, by = "date")
}
ret_index_no_date <- remove_date(ret_index)

### Compute daily returns for govt, equity, futures, cds
price_ret <- calc_returns(ret_index_no_date)

# Store govt, equity, futures, cds returns into a variable (to also store other asset returns later)
all_asset_ret <- price_ret

## FX: returns based on price and funding
fx_strat <- strategies %>% filter(asset_class == "fx")
fx_inst <- fx_strat %>% select(instrument) %>%
  mutate(ticker = paste(instrument, "Curncy"),
         name = instrument) %>%
  unique()

### Download required data from Bloomberg if there are any strategies
if (nrow(fx_inst) > 0) {
  fx_index <- bdh_batch(fx_inst)
  
  fx_price_ret <- calc_returns(fx_index)
  
  # Get currencies required
  required_funding <- c(substr(fx_inst$instrument, 1,3), substr(fx_inst$instrument, 4,6)) %>% unique
  
  # Get tickers of currency fundings
  required_fx_depo <- fx_funding %>% filter(tolower(currency) %in% tolower(required_funding)) %>%
    mutate(name = paste(tolower(currency), "depo", sep ="_"),
           ticker = ticker)
  
  # Download funding rates from Bloomberg
  fx_funding_rates <- bdh_batch(required_fx_depo)
  
  # Funding based on actual/360, hence calculate number of days between dates (to account for weekends)
  day_count <- as.numeric(fx_funding_rates$date - lag(fx_funding_rates$date))

  # Calculate funding return for each day
  fx_funding_ret <- fx_funding_rates %>% remove_date %>%
    .[]/360 * day_count / 100  # rate / (days in year) * day_count / (adjustment for %)
    
  fx_funding_ret <- fx_funding_ret %>%
    mutate_all(funs(lag))   # Lag one day
  
  # Earn the left funding and pay the right funding for the currency pair
  left_funding <- fx_funding_ret[,paste(substr(names(fx_price_ret)[-1], 1, 3), "depo", sep="_")] 
  right_funding <- fx_funding_ret[,paste(substr(names(fx_price_ret)[-1], 4, 6), "depo", sep="_")] 
  total_funding <- left_funding - right_funding  # Earn left pair funding, pay right pair
  
  # Fill NAs for dates without funding (of either pair), may lose return accuracy but allows for calculation in the earlier bits of history
  total_funding[is.na(total_funding)] <- 0

  # Total return is price return + funding return
  fx_total_ret <- remove_date(fx_price_ret) + total_funding
  
  # Combine FX returns with the other asset returns
  all_asset_ret <- cbind(fx_total_ret, price_ret)
}

```

```{r calc_sizes}
###############################################
# COMPUTE SIZE OF STRATEGIES 
###############################################

# Compute unweighted sizes of the strategies (largely to cater to curve and spread trades)
# Unweighted sizes are required to compute active risk of the strategies

###########################################################
# Critical variables in below chunk
###########################################################
## curr_unwt_size       = the relative size of each instrument in the current trade assuming trade is unweighted, 
##                        e.g. Long German 10y vs 2y will approx show a size of 1.0 for 10y and 5.0 for 2y (5 times exposure)
## strat_unwt_size_list = collation of all curr_unwt_size for all trades
## actual_wt            = actual traded/planned sizes for each trade in % of R2, timeseries
## sim_wt               = simulated size (% of R2), ie last size of each trade extrapolated to the entire history, timeseries

## Initialize blank dataframes
strat_unwt_size_list <- list()
actual_wt <- sim_wt <- blank_df

## Iterate through each unique strategy
for (i in unique(strategies$strategy)) {
  curr_unwt_size <- blank_df
  
  # Filter out current strategy
  curr_strat <- strategies %>% filter(strategy == i) 
  inst_list <- curr_strat$instrument %>% unique
  
  # Iterate through all instruments required for this strategy
  
  ## If size is in months
  if (curr_strat$size_type[1] == "months") {
    # Extract necessary duration
    dates <- all_dur$date
    curr_strat_dur <- select(all_dur, inst_list) 
    
    # Compute max duration for every time period
    max_dur <- apply(curr_strat_dur, 1, max)
    
    # Divide by the longest duration
    curr_unwt_size <- curr_strat_dur %>%
      mutate_all(funs(max_dur/.))
    
    actual_wt[i] <- 0
    # Loop through each instrument to compute the sizes
    for (curr_inst in inst_list) {
      curr_inst_df <- filter(curr_strat, instrument == curr_inst) 
      # ....
      curr_unwt_size[[curr_inst]] <- curr_unwt_size[[curr_inst]] * sign(curr_inst_df$size[1])
      
      # Add size for every period of open position, only for first instrument to avoid double counting
      if (curr_inst == inst_list[1]) {
        for (j in 1:nrow(curr_inst_df)) {
          strat_start <- if (is.na(curr_inst_df$open_date[j])) as.Date(today()-days(1)) else curr_inst_df$open_date[j]
          strat_end <- if (is.na(curr_inst_df$close_date[j])) as.Date(today()) else curr_inst_df$close_date[j]
          
          # Sizing is based on maximum duration to accomodate curve trades .....
          actual_wt[i] <- actual_wt[i] + if_else(sim_wt$date <= strat_end & sim_wt$date > strat_start, 
                                                 abs(curr_inst_df$size[j]) / (max_dur * 12), 0) 
        }
      }
    }
    
    # Add back date
    curr_unwt_size <- cbind(date = dates, curr_unwt_size)
    
    # Simulated wt is equal to current open position
    sim_wt[i] <- tail(actual_wt[[i]],1)
  } 
  else { # If size is in percent
    actual_wt[i] <- 0
    for (curr_inst in inst_list) {
      curr_unwt_size[curr_inst] <- 0
      curr_inst_df <- curr_strat %>% filter(instrument == curr_inst)
      
      # Set weight as actual first
      for (j in 1:nrow(curr_inst_df)) {
        # Strat start and end
        strat_start <- if (is.na(curr_inst_df$open_date[j])) as.Date(today()-days(1)) else curr_inst_df$open_date[j]
        strat_end <- if (is.na(curr_inst_df$close_date[j])) as.Date(today()) else curr_inst_df$close_date[j]
        
        actual_wt[i] <- actual_wt[i] + if_else(sim_wt$date <= strat_end & sim_wt$date > strat_start,
                                               abs(curr_inst_df$size[j])/100, 0)
        
        curr_unwt_size[curr_inst] <- curr_unwt_size[curr_inst] + 
          if_else(sim_wt$date <= strat_end & sim_wt$date > strat_start,
                  curr_inst_df$size[j]/100, 0)
      }
    }
    
    # Find max abs size of each row
    if (ncol(curr_unwt_size) > 2) { # If more than 2 columns (incl date)
      row_max <- apply(curr_unwt_size[,-1], 1, function(x) {max(abs(x))})
      divided <- apply(curr_unwt_size[,-1], 2, function(x) {x / row_max})
    } else {
      row_max <- curr_unwt_size[,-1]
      divided <- curr_unwt_size[,-1] / row_max
    }
    
    # Divide each row by its max, if max is 0, resulting in failed division, set weight to zero
    divided[is.nan(divided)] <- NA
    divided_df <- as.data.frame(divided)
    
    # If any in the row is NA, we fill with last available data. 
    # this allows us to compute historical unweighted returns based on current exposure
    for (k in 1:nrow(divided_df)) {
      if (is.na(divided_df[k,1])) {
        divided_df[k,] <- tail(divided_df[!is.na(divided_df[,1]),], 1)
      }
    }
    
    colnames(divided_df) <- names(curr_unwt_size %>% select(-date))
    
    # Recombine divided results to curr_unwt_size
    curr_unwt_size <- cbind(curr_unwt_size %>% select(date), divided_df)
    
    # Weight of strategy is equal to the largest weight for each time period
    actual_wt[i] <- row_max
    
    sim_wt[i] <- tail(actual_wt[[i]],1)
  }
  
  #colnames(curr_unwt_size) <- c("date", inst_list)
  
  strat_unwt_size_list[[i]] <- curr_unwt_size
}

# Resize returns to have same dates as the strategy sizes
ret_resized <- left_join(blank_df,
                         mutate(all_asset_ret, date = as.Date(row.names(all_asset_ret))), by = "date") 

```

```{r calc_returns}
###################################
# Compute returns for each strategy
###################################

###########################################################
# Critical variables in below chunk
###########################################################
## unwt_ret              = unweighted return of each trade by combining the returns across all instruments for the trade, timeseries
## actual_strat_ret_list = actual return, computed by taking (unwt ret) * (actual size)
## sim_strat_ret_list    = simulated return, computed by taking (unwt ret) * (simulated size)
## strat_unwt_size_list  = unweighted size of instruments, explained in above chunk

actual_strat_ret_list <- list()
sim_strat_ret_list <- list()
unwt_ret <- blank_df

# Iterate through all strategies
for (i in 1:length(strat_unwt_size_list)) {
  # Extract out current strategy
  each_strategy <- strat_unwt_size_list[[i]]

  # Select only the necessary asset returns
  required_ret <- ret_resized %>% select(colnames(each_strategy))
  
  # Compute unwted return for each asset 
  unwt_ret[names(strat_unwt_size_list)[i]] <- (select(required_ret, -date) * select(each_strategy, -date)) %>%
    rowSums()

}

# Calculate actual and simulated return
actual_ret <- remove_date(unwt_ret) * remove_date(actual_wt)
sim_ret <- remove_date(unwt_ret) * remove_date(sim_wt)
```

```{r get_scenarios}
scenarios_input <- read.csv("inputs/scenarios.csv", stringsAsFactors = FALSE) %>%
  mutate(start_date = ymd(start_date),
         end_date = ymd(end_date))

# Add permanent series of most recent quarter
scenarios <- rbind(scenarios_input, 
      data.frame(period = c("Last3M"), start_date = c(today() - months(3)), end_date = c(as.Date(NA))))

# Order by last 3M, then based on start dates (for plotting purposes)
ordered_periods <- c("Last3M", scenarios$period[order(scenarios$start_date)][!scenarios$period[order(scenarios$start_date)] %in% c("Last3M")])
```

```{r calc_active_risk}
# We want to calculate active risk for this quarter, as well as last quarter

# Assume current weights to be the last available day's weight ie today
curr_wt <- tail(sim_wt[,active_strategies],1) 

# Find weights of previous strat, assumed to be the position 3 months ago (likely to be round strat time)
t_lastq <- today() - months(3)  # Find date exactly 3 months ago
date_lastq <- sim_wt$date[min(which(sim_wt$date > t_lastq))]  # Find date closest to the 3 month ago exact date
prev_wt <- tail(actual_wt %>% filter(date == date_lastq)) %>%   # Set previous wt to 3m ago, remove strategies with size of 0
  gather(strat, size, -date) %>% 
  filter(size != 0) %>%
  spread(strat, -date) %>%
  select(-date)

# Calc active risk for current strategies
curr_strat_df <- apply(scenarios,1, function(x) {calc_active_risk(unwt_ret, curr_wt, x['start_date'], x['end_date'])})
names(curr_strat_df) <- scenarios$period
active_risk_all <- sapply(curr_strat_df, function(x) x$active_risk) %>% 
  as.data.frame %>%
  rownames_to_column("strategy")

# Calc active risk for last quarter strategies
prev_strat_df <- calc_active_risk(unwt_ret, prev_wt, date_lastq - months(3), date_lastq)
prev_strat_active_risk <- sum(abs(prev_strat_df$active_risk)) * 10000

``` 

```{r calc_team_correlation_analysis}
# Calculate team returns by summing returns across strategies within each division
team_ret <- sim_ret %>% 
  rownames_to_column("date") %>%
  gather(strategy, return, -date) %>%
  left_join(strategies %>% select(strategy, owner), 
            by = "strategy") %>%
  mutate(strategy = str_extract(strategy, "^.*(?=:::)")) %>%
  group_by(date, owner) %>%
  summarise(return = sum(return, na.rm = T)) %>% 
  spread(owner, -date)

# Calculate correlation between teams, see helper.R for calc_cor()
team_cor <- calc_cor(team_ret, 
                     start_date = scenarios %>% filter(period == "Last3M") %>% .$start_date) 

```

```{r write_up}
###################################################
# Start generation of report, starting with writeup
###################################################

# Parameters to be displayed in later section
risk_budget <- 80
current_quarter <- month(today()) %/% 3 + 1
prev_quarter <- if (month(today()) %/% 3 == 0) 4 else month(today()) %/% 3
current_active_risk <- active_risk_all$Last3M %>% abs %>% sum * 10000
prev_active_risk <- prev_strat_active_risk
info_ratio <- 0.3
gfc_active_risk <- active_risk_all$GFCStress %>% abs %>% sum * 10000
taper_active_risk <- active_risk_all$TaperTantrum %>% abs %>% sum * 10000

# Find highest active risk strategy
top_strategy <- active_risk_all %>% select(strategy, Last3M) %>% arrange(desc(Last3M)) %>% head(1)
top_strategy_risk <- top_strategy$Last3M / sum(active_risk_all$Last3M)
top_strategy_name <- top_strategy$strategy %>% str_extract("^.*(?=:::)")
top_strategy_owner <- top_strategy$strategy %>% 
  str_extract("(?<=:::).*$") %>%
  toupper
top_strategy_type <- strategies %>% filter(strategy == top_strategy$strategy) %>% .$type

# Find most diversifying strategy
most_diverse <- active_risk_all %>% select(strategy, Last3M) %>% arrange(desc(Last3M)) %>% tail(1)
most_diverse_risk <- most_diverse$Last3M / sum(active_risk_all$Last3M)
most_diverse_name <- most_diverse$strategy %>% str_extract("^.*(?=:::)")
most_diverse_owner <- most_diverse$strategy %>%
  str_extract("(?<=:::).*$") %>%
  toupper

# Format active risk table (by strategies)
strat_active_risk <- active_risk_all %>% 
  select(strategy, Last3M) %>% 
  left_join(strategies %>% select(strategy, owner, asset_class, type) %>% unique, by = "strategy")

# Calculate active risk by division
div_risk <- strat_active_risk %>%
  group_by(owner) %>%
  summarise(Last3M = sum(abs(Last3M))) %>%
  ungroup %>%
  mutate(risk_percent = Last3M / sum(Last3M),
         owner = toupper(owner)) %>%
  arrange(desc(risk_percent))

```

**The RMD ex BW active risk utilization for Q`r current_quarter` is expected to be around `r sprintf("%.1f", current_active_risk)`bps in our baseline scenario**, `r if (current_active_risk > risk_budget) "above" else "below"` the available risk budget for FY18/19 and `r if (current_active_risk > prev_active_risk) "above" else "below"` our estimates for the last quarters (`r prev_quarter`Q: `r sprintf("%.1f",prev_strat_active_risk)`bps). Assuming an information ratio of `r sprintf("%.1f", info_ratio)`, the expected portfolio excess return will be `r sprintf("%.1f", info_ratio * current_active_risk)` (annualized). Under a stress scenario similar to the GFC and the Taper Tantrum, we expect active risk utilization to increase to around `r sprintf("%.1f", gfc_active_risk)` and `r sprintf("%.1f", taper_active_risk)`bps respectively

**Key observations are: **

1. `r top_strategy_owner`'s `r top_strategy_type` strategy of `r top_strategy_name` constitutes the highest active risk. The trade has an active risk of `r sprintf("%.1f", top_strategy$Last3M * 10000)`bps, which is `r sprintf("%.1f", top_strategy_risk * 100)`% of total active risk

2. The most diversifying strategy in the portfolio is the `r most_diverse_name` from the `r most_diverse_owner`, with a `r sprintf("%.1f", most_diverse_risk * 100)`% risk contribution

3. Risk contribution across the different divisions are shown below. `r div_risk$owner[1]` accounts for bulk of total risk at `r sprintf("%.1f", div_risk$risk_percent[1] * 100)`%, followed by `r div_risk$owner[2]` and `r div_risk$owner[3]` at `r sprintf("%.1f", div_risk$risk_percent[2] * 100)`% and `r sprintf("%.1f", div_risk$risk_percent[3] * 100)`% respectively. 

### Current Active Strategies

```{r display_strategies}
# Find current weight
wt_df <- data.frame(size_percent = t(curr_wt)) %>% 
  rename(size_percent = 1) %>% 
  rownames_to_column("strategy") 

# Process and print strategies
strategies %>%                                                         # Get strategies
  filter(strategy %in% active_strategies & is.na(close_date)) %>%      # Filter strategies still open
  group_by(owner, strategy, type, size_type, instrument) %>%           # Sum up trade sizes for each strategies' instrument
  summarise(size = sum(size)) %>%
  group_by(owner, type, strategy, size_type) %>%                       # Find size of trade by taking the max (in case of long short)
  summarise(size = max(size)) %>%
  left_join(wt_df, by = "strategy") %>%                                # Add current weight of each strat to the table
  left_join(active_risk_all %>% select(strategy, active_risk = Last3M), by = "strategy") %>%  # Add active risk
    ungroup %>%                             
  mutate(active_risk_percent = active_risk / sum(active_risk),         # Calculate % of active risk, and reformat active risk in bps 
         active_risk = active_risk * 10000) %>%
    ungroup %>%
  arrange(desc(active_risk)) %>%                                       # Sort strategies in descending by active risk
  mutate(input_size = str_replace(sprintf("%.2f %s", size, size_type)," percent","%") %>% str_replace(" months", "m"),  # Format numbers
         size_percent = scales::percent(size_percent,accuracy = 0.01),
         active_risk = scales::number(active_risk, accuracy = 0.1),
         active_risk_percent = scales::percent(active_risk_percent, accuracy = 0.1)) %>%
  mutate(strategy = str_extract(strategy, "^.*(?=:::)"),               # Format naming of strategy to remove division, add serial number
         no = 1:nrow(.)) %>%
  select(no, strategy, owner, type, input_size, size_percent, active_risk, active_risk_percent) %>%   # Select required fields for display
  rename("active_risk (bps)" = "active_risk",                          # Format headers of the table
         "active_risk (% R2)" = "active_risk_percent") %>% 
  kable                                                                # Display table
  
```

## Active Risk

*Active risk contribution is the contribution to total standard deviation of the portfolio. Individual trades' active risk is additive to form overall portfolio standard deviation aka active risk of the portfolio*

```{r display_active_risk, fig.width = 9, fig.height = 4}
# Find order of strategies by their risk contribution in the last 3m (for plotting purposes)
ordered_strategies <- select(active_risk_all, strategy, Last3M)  %>%
  rename(active_risk = "Last3M") %>%
  mutate(strategy = str_extract(strategy, "^.*(?=:::)")) %>%
  group_by(strategy) %>%
  summarise(active_risk = sum(active_risk)) %>%
  ungroup %>%
  mutate(order = order(active_risk)) %>%
  arrange(active_risk) %>%
  .$strategy

# Formating active risk for display and to fit into ggplot
active_risk_gathered <- active_risk_all %>%
  left_join(unique(select(strategies, strategy, owner, type)), by = "strategy") %>%
  mutate(strategy = str_extract(strategy, "^.*(?=:::)")) %>%
  mutate(strategy = factor(strategy, level = ordered_strategies),
         owner = factor(owner, level = c("us", "cat", "europe", "ed"))) %>%
  gather(period, active_risk, -strategy, -owner, -type) %>%
  mutate(period = factor(period, level = ordered_periods))

# Plot active risk by strategy
ggplot(active_risk_gathered, aes(x = strategy, y = active_risk * 10000, fill = owner)) + 
  geom_col() +
  facet_wrap(~period, ncol = 3) +
  labs(y = "active risk (bp)", title = "Active Risk by Strategy") +
  coord_flip() 
```
```{r display_active_risk_2, fig.width = 9, fig.height = 2}
# Plot active risk by asset strategies
active_risk_gathered %>% 
  group_by(period, type) %>%
  summarise(active_risk = sum(abs(active_risk))) %>%
  sort_gg("type", "active_risk") %>%
  ggplot(aes(x = type, y = active_risk * 10000)) + 
  geom_col() +
  facet_wrap(~period, ncol = 3) +
  labs(y = "active risk (bp)", title = "Active Risk by Strategy Types") +
  coord_flip() 

# Plot active risk by asset class
asset_types <- data.frame(type = c("Curve", "Inflation", "Duration", "Spread", "FX", "Equity"), 
                          asset_class = c("Fixed Income", "Fixed Income", "Fixed Income", "Fixed Income", "FX", "Equity"), 
                          stringsAsFactors = FALSE) 

active_risk_gathered %>% 
  left_join(asset_types, by = "type") %>%
  mutate(asset_class = ifelse(is.na(asset_class), "Others", asset_class)) %>%
  group_by(period, asset_class) %>%
  summarise(active_risk = sum(abs(active_risk))) %>%
  sort_gg("asset_class", "active_risk") %>%
  ggplot(aes(x = asset_class, y = active_risk * 10000)) + 
  geom_col() +
  facet_wrap(~period, ncol = 3) +
  labs(y = "active risk (bp)", title = "Absolute Active Risk by Asset Class") +
  coord_flip() 

# Plot active risk by division
active_risk_gathered %>% 
  group_by(period, owner) %>%
  summarise(active_risk = sum(abs(active_risk))) %>%
  sort_gg("owner", "active_risk") %>%
  ggplot(aes(x = owner, y = active_risk * 10000)) + 
  geom_col() +
  facet_wrap(~period, ncol = 3) +
  labs(y = "active risk (bp)", title = "Absolute Active Risk by Division") +
  coord_flip() 
```


```{r calc_sharpe}
# Find unique_strategies
unique_strategies <- strategies %>%
  select(strategy, owner, type) %>%
  unique

# Start date for calculation of returns
start_date_returns <- as.Date("2018-01-01")

# Extract return data based on start_date
actual_ret_filtered <- actual_ret %>% 
  rownames_to_column("date") %>%
  filter(date > start_date_returns) %>%
  gather(strategy, pnl, -date) %>%
  left_join(unique_strategies, by="strategy")
 
# Calculate sharpe grouped by owner, in annualized bps of R2
sharpe_by_owner <- actual_ret_filtered %>% 
  group_by(owner) %>%
  summarise(return = mean(pnl, na.rm = T) * 250 * 10000, 
            std_dev = sd(pnl, na.rm = T) * sqrt(250) * 10000) %>%
  mutate(sharpe = round(return / std_dev ,2),
         return = round(return, 2),
         std_dev  = round(std_dev , 2)) 

# Calculate sharpe grouped by strategy, in annualized bps of R2
sharpe_by_strategy <- actual_ret_filtered %>%
  group_by(type) %>%
  summarise(return = mean(pnl, na.rm = T) * 250 * 10000, 
            std_dev  = sd(pnl, na.rm = T) * sqrt(250) * 10000) %>%
  mutate(sharpe = round(return / std_dev , 2),
         return = round(return, 2),
         std_dev  = round(std_dev , 2))
```

## Sharpe Ratio

*Sharpe Ratio = Return / Std_dev*

*The returns and standard deviation below have been computed as annualized return in weighted basis points of R2.*

### 2018 Year-to-Date

#### By division
`r kable(sharpe_by_owner)`

#### By strategy types
`r kable(sharpe_by_strategy)`

#### Sharpe ratio breakdown by division

```{r display_sharpe, fig.width = 9}
# Breakdown components of sharpe (return and standard dev)
sharpe_breakdown <- actual_ret_filtered %>%
  group_by(owner, strategy, type) %>%
  summarise(std_dev = sd(pnl, na.rm = T) * sqrt(250) * 10000,
            return = mean(pnl, na.rm = T) * 250 * 10000) %>%
  ungroup %>%
  mutate(strategy = str_extract(strategy, "^.*(?=:::)")) %>%
  arrange(owner, return) %>%
  mutate(strategy = factor(strategy, levels = unique(strategy)))

# Plot breakdown of returns
sharpe_breakdown %>% 
  ggplot(aes(x = strategy, y = return)) + 
  geom_col() + 
  facet_wrap(~owner, ncol = 2, scales = "free_y") + 
  coord_flip() +
  labs(title = "Return contribution of trades (bps of R2, annualized)")

# Sort by standard deviation
sharpe_breakdown2 <- sharpe_breakdown %>%
  arrange(owner, std_dev) %>%
  mutate(strategy = factor(strategy, levels = unique(strategy))) 

# Plot breakdown of standard deviation
sharpe_breakdown2 %>% ggplot(aes(x = strategy, y = std_dev)) + 
  geom_col() + 
  facet_wrap(~owner, ncol = 2, scales = "free_y") + 
  coord_flip() +
  labs(title = "Std dev of trades (bps of R2, annualized)")
```

## Correlations

### Team Correlations

```{r display_correlation}
# Plot correlation of returns between teams
team_cor %>%
  plot_cor(title = NULL)
```

### Strategy Correlations

```{r display_corr_heatmap, fig.width = 9, fig.height = 5}
# Plot correlation of returns between strategies

#Find strategies ordered by owner name (for plotting purposes)
ordered_strategies <- strategies %>% select(strategy, owner) %>%
  mutate(strategy = str_extract(strategy, "^.*(?=:::)")) %>%
  arrange(owner, strategy) %>%
  .$strategy %>%
  unique

# Extract unweighted return of all strategies still open
uniq_unwt_ret <- unwt_ret[,c("date", active_strategies)] %>%
  gather(strategy, return, -date) %>% 
  mutate(strategy = str_extract(strategy, "^.*(?=:::)")) %>%
  unique %>% 
  spread(strategy, -date) 

# Calculate correlation between all open trades across all scenarios
strat_cor_all <- bind_rows(
  apply(scenarios, 1,  # "Loop" through all scenarios
        function(x)
          # Calculate correlation for each  scenario
          calc_cor(uniq_unwt_ret, start_date = x['start_date'], end_date = x['end_date'], period_name = x['period']))) %>%
  mutate(strat1 = factor(strat1, levels = ordered_strategies),   # Order strategies for plotting
         strat2 = factor(strat2, levels = ordered_strategies))

# Plot all correlation matrices
for (i in rev(unique(strat_cor_all$period))) {
  cor_df <- strat_cor_all %>% filter(period == i)
  plot_cor(cor_df,  paste("Correlation during", i))
}

```

## Performance of strategies

### Actual returns (Cumulative Rolling 12 months)

```{r display_actual_ret, fig.width = 9}
# Plot actual returns, starting from start_date_returns, defined when calculating sharpe ratio
actual_ret_filtered <- actual_ret %>%
  rownames_to_column("date") %>%
  filter(date > start_date_returns) %>%
  column_to_rownames("date")

actual_ret_filtered[is.na(actual_ret_filtered)] <- 0    # Set all NAs to 0, to facilitate summing

# Find cumulative sum of returns
actual_ret_cum <- actual_ret_filtered %>%               
  mutate_all(funs(cumsum)) %>% 
  mutate(date = as.Date(rownames(actual_ret_filtered)))

# Format cumulative return for plotting  
actual_ret_cum_gathered <- actual_ret_cum %>%
  gather(strategy, cum_pnl, -date) %>%
  mutate(owner = str_extract(strategy, "(?<=:::).*$"),
         strategy = str_extract(strategy, "^.*(?=:::)"),
         cum_pnl = cum_pnl * 10000) 

# Plot cumulative return, one chart for each owner
results <- lapply(unique(actual_ret_cum_gathered$owner), function(i) {
  g <- actual_ret_cum_gathered %>% 
    filter(owner == i) %>%                                  # Filter returns from current owner
    ggplot(aes(x = date, y = cum_pnl)) +       
    geom_area(aes(fill = strategy)) +                       # Plot area chart
    stat_summary(fun.y = sum, geom = "line", size = 1) +    # Plot total line 
    labs(y = "Cumulative Pnl (R2 wt bps)", title = i) +
    theme(axis.title.x = element_blank(), legend.position = "bottom")
  print(g)
})
```

### Historical simulated returns profile of strategies

Below are 3 month returns arising from current strategies extrapolated into history. Higher intensive of green/red indicates a larger positive profit/loss over a 3 month period, while white indicates no significant PnL impact. Grey indicates the underlying instrument/s was not available during the period

*Unweighted return is the strategy's return over its own notional size. For curve trades, the notional of the higher duration leg is taken to be the trade size. This allows us to have an idea how each strategy would have performed over different periods in history*

```{r display_returns_over_time, fig.width = 9}
window = 20 * 3
######################################
#  Compute rolling 3 month returns
######################################

unwt_ret_roll <- apply(remove_date(unwt_ret), 2, roll_sum, n = window) %>% as.data.frame
unwt_ret_roll <- cbind(data.frame(date = unwt_ret$date[-(1:(window-1))]), unwt_ret_roll)

sim_ret2 <- sim_ret %>% rownames_to_column("date") %>%
  mutate(date = as.Date(date))
sim_ret_roll <- apply(remove_date(sim_ret2), 2, roll_sum, n = window) %>% as.data.frame
sim_ret_roll <- cbind(data.frame(date = sim_ret2$date[-(1:(window-1))]), sim_ret_roll)

######################################
# Plot heatmap of returns across time
######################################

active_unwt_ret_roll <- unwt_ret_roll[,c("date", active_strategies)]

max_ret_unwt <- max(remove_date(active_unwt_ret_roll), na.rm = T)
min_ret_unwt <- min(remove_date(active_unwt_ret_roll), na.rm = T)

# Adjusting x-axis to display dates properly
recalc_date <- active_unwt_ret_roll %>% 
  select(date) %>%
  mutate(yr = year(date), factored_date = as.factor(date)) %>%
  group_by(yr) %>%
  mutate(first_day = min(date)) %>%
  ungroup %>%
  mutate(new_date = ifelse(first_day == date & yr > 1994, sprintf("%02d", yr %% 100), ""),
         row_date = row_number()) %>%
  filter(new_date != "")
  
break_positions <- which(recalc_date$new_date != "")
date_labels <- recalc_date %>%
  filter(new_date != "") %>%
  .$new_date

active_unwt_ret_roll %>% 
  gather(strategy, ret_3m, -date) %>% 
  mutate(owner = str_extract(strategy, "(?<=:::).*$")) %>%
  arrange(owner, strategy) %>%
  mutate(strategy = factor(strategy, levels = unique(strategy))) %>%
  mutate(date = as.factor(date)) %>%
  ggplot(aes(x = date, y = strategy)) +
  geom_tile(aes(fill = ret_3m)) +
  scale_fill_gradientn(colours = c("#F70000", "#FF4040", "#FA6C6C","white", "lightgreen", "green","darkgreen"),
                       values = rescale(c(c(1, 0.3, 0.1) * min_ret_unwt, 0, c(0.1, 0.3, 1) * max_ret_unwt), to = c(0,1)),
                       labels = scales::percent(c(-0.2, 0, 0.2), accuracy =1),
                       breaks = c(-0.2, 0, 0.2)) +
  scale_x_discrete(labels = date_labels, breaks = recalc_date$factored_date) +
  labs(title = "Unweighted 3m return (% of notional)") +
  theme(legend.position = "bottom", axis.title = element_blank())

```

*Weighted return is assuming current strategy sizes extrapolated into history to calculate the return contribution of each of the strategies based on different periods in history. Consistent light shades of colours across all periods in history could indicate the trade is sized too small for its historical volatility*

```{r display_weighted_returns_timeline, fig.width = 9}

######################################
# Plot heatmap of weighted simulated returns
######################################

# Adjusting x-axis to display dates properly
recalc_date <- sim_ret_roll %>% 
  select(date) %>%
  mutate(yr = year(date), factored_date = as.factor(date)) %>%
  group_by(yr) %>%
  mutate(first_day = min(date)) %>%
  ungroup %>%
  mutate(new_date = ifelse(first_day == date & yr > 1994, sprintf("%02d", yr %% 100), ""),
         row_date = row_number()) %>%
  filter(new_date != "") 

break_positions <- which(recalc_date$new_date != "")
date_labels <- recalc_date %>%
  filter(new_date != "") %>%
  .$new_date

max_ret_wt <- max(remove_date(sim_ret_roll), na.rm = T) * 10000
min_ret_wt <- min(remove_date(sim_ret_roll), na.rm = T) * 10000

sim_ret_roll %>% 
  select(date, active_strategies) %>%
  mutate(date = as.factor(date)) %>%
  gather(strategy, ret_3m, -date) %>%
  mutate(owner = str_extract(strategy, "(?<=:::).*$")) %>%
  arrange(owner, strategy) %>%
  mutate(strategy = factor(strategy, levels = unique(strategy)),
         ret_3m = ret_3m * 10000) %>%  
  ggplot(aes(x = date, y = strategy)) +
  geom_tile(aes(fill = ret_3m)) +
  scale_fill_gradientn(colours = c("#F70000", "#FF4040", "#FA6C6C","white", "lightgreen", "green","darkgreen"),
                       values = rescale(c(c(1, 0.3, 0.1) * min_ret_wt, 0, c(0.1, 0.3, 1) * max_ret_wt), to = c(0,1)),
                       labels = scales::number(c(-10, 0, 10), accuracy =1),
                       breaks = c(-10, 0, 10)) +
  scale_x_discrete(labels = date_labels, breaks = recalc_date$factored_date) +
  labs(title = "Weighted 3m return (bp of R2)") +
  theme(legend.position = "bottom", axis.title = element_blank())
  
```

