---
title: "SAT Active Risk Report (Reduced)"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(tidyverse)
library(Rblpapi)
library(lubridate)
library(knitr)
library(tidymas)
library(ggpubr)

blpConnect()
```

```{r build_portfolios_and_get_return, message = FALSE}
# Get strategies from file and their sizes (mix of month weighted and %)
strategies_list <- build_strategies("../data2/strategies_reduced.csv")

# Get required instruments and portfolios (actual vs sim)
instr_df <- strategies_list$summary
portfolios_list <- strategies_list[names(strategies_list) != "summary"]

# Get duration from Bloomberg
dur_df <- get_dur_bbg(instr_df)

# Calculate all weights in %
clean_pf_list <- map(portfolios_list, 
                  ~convert_dur_size(., instr_df, dur_df))

# Get returns of assets from Bloomberg
asset_return <- get_ret_bbg(instr_df)

# Calculate weight return of strategies
wt_return <- map(clean_pf_list, 
                  ~calc_strat_wt_return(., asset_return))

# Calculate weight of strategies
strat_headline_size <- map(clean_pf_list, 
                           ~calc_strat_headline_size(.))

# Calculate unweighted return of strategies
unwt_return <- calc_strat_unwt_return(wt_return$sim, strat_headline_size$sim)
```

```{r get_scenarios}
# Set dates for analysis
curr_date <- today()
prev_date <- curr_date - months(3)

# Create scenarios for analysis
scenarios_input <- read.table(
  text = "period,       start_date, end_date
          TaperTantrum, 2013-05-31, 2013-12-31
          GFCStress,    2007-10-31, 2009-02-27", 
  sep = ",", header = TRUE, strip.white = TRUE, colClasses = c("character", "Date", "Date")) 

# Add series of most recent quarter
scenarios <- rbind(scenarios_input, 
      data.frame(period = c("Last3M"), start_date = c(curr_date - months(3)), end_date = c(curr_date))) 

rownames(scenarios) <- scenarios$period 

# Order by last 3M, then based on start dates (for plotting purposes)
ordered_periods <- c("Last3M", scenarios$period[order(scenarios$start_date)][!scenarios$period[order(scenarios$start_date)] %in% c("Last3M")])

# Get current strategies
curr_strat <- get_strat_size(strat_headline_size$actual, curr_date)
# prev_strat <- get_strat_size(strat_headline_size$actual, prev_date)
# 
# # Calculate active risk of previous quarters strategies 
# active_risk_prev <- calc_active_risk(unwt_return, 
#                                 prev_strat,
#                                 start_date = prev_date - months(3), end_date = prev_date)

# Calculate active risk of current strategies
active_risk_curr <- apply(scenarios, 1, 
                     function(x) {
                       calc_active_risk(unwt_return, 
                                        curr_strat,
                                        start_date = x['start_date'], end_date = x['end_date'])
                     })

# calculate historical return based on scenario dates with current strategy
scenario_return <- apply(scenarios, 1, 
                           function(x) {
                             simulate_history(unwt_return, 
                                      curr_strat, 
                                      x['start_date'], x['end_date'])
                           })
```

## Active risk

```{r active_risk}
# Parameters to be displayed in later section
current_quarter <- ceiling(month(curr_date) / 3)
prev_quarter <- (current_quarter + 2) %% 4 + 1
current_abs_active_risk <- active_risk_curr$Last3M$active_risk %>% abs %>% sum * 10000
info_ratio <- 0.3
gfc_abs_active_risk <- active_risk_curr$GFCStress$active_risk %>% abs %>% sum * 10000
taper_abs_active_risk <- active_risk_curr$TaperTantrum$active_risk %>% abs %>% sum * 10000
max_risk <- max(gfc_abs_active_risk, taper_abs_active_risk)

# Format active risk table (by strategies)
strat_active_risk <- active_risk_curr$Last3M %>%  
  left_join(unique(select(instr_df, strategy, owner, type)), by = "strategy") %>%
  mutate(risk_percent = active_risk / sum(active_risk) * 100, 
         active_risk = active_risk * 10000,
         owner = toupper(owner),
         name = str_extract(strategy, "^.*(?=:::)")) %>%
  arrange(desc(risk_percent))
```

The suite of RMD active strategies is likely to utilise `r sprintf("%.1f", current_abs_active_risk)`bps of active risk budget if fully implemented. Should correlations increase during stress episodes, the active risk utilisation could potentially rise to about `r sprintf("%.1f", max_risk)`bps. We expect these strategies to deliver about `r sprintf("%.1f", info_ratio * current_abs_active_risk)`bps based on RMD's long-term expected information ratio of `r sprintf("%.1f", info_ratio)`


```{r display_strategies}
# Get strategies sizes in %
strat_percent_size <- get_strat_size(strat_headline_size$actual, curr_date) %>%
  rename(size_percent = size)

# Extract necessary portfolio information
pf_overview <- pf_summary(portfolios_list$actual, curr_date) %>%
  select(-date) %>%
  gather(strategy, size) %>%
  left_join(unique(select(instr_df, strategy, size_type, owner, type)), by = "strategy") %>%
  left_join(strat_percent_size, by = "strategy") %>% 
  left_join(select(strat_active_risk, strategy, active_risk, risk_percent), by = "strategy") %>% 
  arrange(desc(active_risk)) 

# Format and print portfolio information
pf_overview %>%
  mutate(size = str_replace(sprintf("%.2f %s", size, size_type)," percent","%") %>% str_replace(" months", "m"),  # Format numbers
         size_percent = scales::percent(size_percent,accuracy = 0.01),
         active_risk = scales::number(active_risk, accuracy = 0.1),
         risk_percent = scales::percent(risk_percent/100, accuracy = 0.1)) %>%
  mutate(strategy = str_extract(strategy, "^.*(?=:::)"),               # Format naming of strategy to remove division, add serial number
         no = 1:nrow(.)) %>%
  select(no, strategy, type, size, size_percent, active_risk, risk_percent) %>%   # Select required fields for display
  rename("active_risk (bps)" = "active_risk",                          # Format headers of the table
         "active_risk (% R2)" = "risk_percent") %>% 
  kable                                                                # Display table
```

## Correlations

### Strategy Correlations

```{r display_corr_heatmap, fig.width = 9, fig.height = 5}
# Plot correlation of returns between strategies

# Extract unweighted return of all strategies still open
uniq_unwt_ret <- unwt_return %>%
  filter(strategy %in% curr_strat$strategy) %>%
  mutate(strategy = str_extract(strategy, "^.*(?=:::)")) %>%
  group_by(date, strategy) %>%
  summarise(return = mean(return, na.rm = TRUE)) %>%
  ungroup 

# Calculate correlation between all open trades across all scenarios
strat_cor_all <- 
  apply(scenarios, 1,  # "Loop" through all scenarios
        function(x)
          # Calculate correlation for each  scenario
          calc_cor(uniq_unwt_ret %>% spread(strategy, return), start_date = x['start_date'], end_date = x['end_date'], period_name = x['period']))# %>%

# Plot all correlation matrices
cor_df <- strat_cor_all$Last3M
plot_cor(cor_df, "Correlation")


write.csv(strat_cor_all$Last3M %>% select(-period) %>% spread(strat2, corr), "active_risk_reduced_output.csv")
print("correlation output to csv file: active_risk_reduced_output.csv")
```
