---
title: "Daily Monitor"
output:
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("C:\\Users\\ylim\\Documents\\R projects\\tidymas\\R\\convenience.R")
```

## Themes for 18Q2
- Low vol world is over (DB), but actually BLK says otherwise

# UK

## GBPUSD

```{r GBPUSD}
g1 <- ggTS("GBPUSD Curncy")
g2 <- ggTS("GBPEUR Curncy")
g3 <- ggTS("UKTWBROA Index", title = "BoE Broad FX index")
grid.arrange(g1, g2, g3, nrow = 2)
```

## UK Nominal Yields

```{r UK_yields}
uk_2y <- ggTS("GTGBP2Y Govt", yield_mode = TRUE)
uk_5y <- ggTS("GTGBP5Y Govt", yield_mode = TRUE)
uk_10y <- ggTS("GTGBP10Y Govt", yield_mode = TRUE)
uk_30y <- ggTS("GTGBP30Y Govt", yield_mode = TRUE)
grid.arrange(uk_2y, uk_5y, uk_10y, uk_30y, nrow = 2)
```

## UK Breakevens
```{r uk_breakevens}
uk_5y_r <- ggTS("UKGGBE05Y Index", yield_mode = TRUE)
uk_10y_r <- ggTS("UKGGBE10Y Index", yield_mode = TRUE)
uk_30y_r <- ggTS("UKGGBE30Y Index", yield_mode = TRUE)
grid.arrange(blank_chart(), uk_5y_r, uk_10y_r, uk_30y_r, nrow = 2)
```

## UK Equities
```{r UK_equities}
ftse100 <- ggTS("UKX Index", title = "FTSE 100")
ftse250 <- ggTS("MCX Index", title = "FTSE 250")
ftse_all <- ggTS("ASX Index", title = "FTSE All Share")
grid.arrange(ftse100, ftse250, ftse_all, nrow = 2)
```

# Europe

## EUR

```{r EURUSD}
g1 <- ggTS("EURUSD Curncy")
g2 <- ggTS("EURGBP Curncy")
grid.arrange(g1, g2, nrow = 2)
```

## German Nominal Yields

```{r DEM_yields}
dem_2y <- ggTS("GTDEM2Y Govt", yield_mode = TRUE)
dem_5y <- ggTS("GTDEM5Y Govt", yield_mode = TRUE)
dem_10y <- ggTS("GTDEM10Y Govt", yield_mode = TRUE)
dem_30y <- ggTS("GTDEM30Y Govt", yield_mode = TRUE)
grid.arrange(dem_2y, dem_5y, dem_10y, dem_30y, nrow = 2)
```

## Core Europe Equities
```{r core_ez_equities}
sx5e <- ggTS("SX5E Index", title = "EuroStoxx")
dax <- ggTS("DAX Index", title = "German DAX")
cac <- ggTS("CAC Index", title = "France CAC")
smi <- ggTS("SMI Index", title = "Swiss SMI")
grid.arrange(sx5e, dax, cac, smi, nrow = 2)
```

## Periphery Europe Equities
```{r peri_ez_equities}
ibex <- ggTS("IBEX Index", title = "Spain IBEX")
mib <- ggTS("FTSEMIB Index", title = "Italy MIB")
psi <- ggTS("BVLX Index", title = "Portugal PSI")
ase <- ggTS("ASE Index", title = "Greece ASE")
grid.arrange(ibex, mib, psi, ase, nrow = 2)
```

# Volatility

## Volatility
```{r vol}
vix <- ggTS("VIX Index", title = "VIX")
v2x <- ggTS("V2X Index", title = "VSTOXX")
vdax <- ggTS("V1X Index", title = "VDAX")
vftse <- ggTS("VFTSE Index", title = "VFTSE")
grid.arrange(vix, v2x, vdax, vftse, nrow = 2)
```

## Commodities
```{r commods}
wti <- ggTS("CL1 Comdty", title = "WTI 1st contract")
brent <- ggTS("CO1 Comdty", title = "Brent 1st contract")
gold <- ggTS("XAU Curncy", title = "Gold")
silver <- ggTS("XAG Curncy", title = "Silver")
corn <- ggTS("C 1 Comdty", title = "Corn")
wheat <- ggTS("W 1 Comdty", title = "Wheat")
grid.arrange(wti, gold, corn, brent, silver, wheat, ncol = 3)
```

# Select Equities

## US Indices
```{r us_indices}
spx <- ggTS("SPX Index", title = "S&P500")
dow_jones <- ggTS("INDU Index", title = "Dow Jones")
nasdaq <- ggTS("CCMP Index", title = "NASDAQ Composite")
russell_2000 <- ggTS("RTY Index", title = "Russell 2000")
grid.arrange(spx, dow_jones, nasdaq, russell_2000, nrow = 2)
```

## FAANGS

```{r FAANGS}
facebook <- ggTS("FB US Equity", title = "Facebook")
apple <- ggTS("AAPL US Equity", title = "Apple")
amazon <- ggTS("AMZN US Equity", title = "Amazon")
netflix <- ggTS("NFLX US Equity", title = "Netflix")
google <- ggTS("GOOG US Equity", title = "Alphabet")
grid.arrange(facebook, apple, amazon, netflix, google, ncol = 3)
```

## Tech - special interest
```{r tech_special}
tsla <- ggTS("TSLA US Equity", title = "Tesla")
spotify <- ggTS("SPOT US Equity", title = "Spotify")
grid.arrange(tsla, spotify)
```

## Tech - Software & Services

```{r tech_soft}
msft <- ggTS("MSFT US Equity", title = "Microsoft")
visa <- ggTS("V US Equity", title = "Visa")
oracle <- ggTS("ORCL US Equity", title = "Oracle")
ma <- ggTS("MA US Equity", title = "Mastercard")
salesforce <- ggTS("CRM US Equity", title = "SalesForce")
ibm <- ggTS("IBM US Equity", title = "IBM")
grid.arrange(msft, visa, oracle, ma, salesforce, ibm, ncol = 3)
```

## Tech - Hardware & Equipment

```{r tech_hardware}
csco <- ggTS("CSCO US Equity", title = "CISCO")
grid.arrange(csco)
```


## Tech - Semiconductors & Equipment

```{r tech_semicon}
intc <- ggTS("INTC US Equity", title = "Intel")
nvda <- ggTS("NVDA US Equity", title = "Nvidia")
amd <- ggTS("AMD US Equity", title = "AMD")
micron <- ggTS("MU US Equity", title = "Micron")
txn <- ggTS("TXN US Equity", title = "Texas Instrument")
amat <- ggTS("AMAT US Equity", title = "Applied Materials")
grid.arrange(intc, nvda, amd, micron, txn, amat, nrow = 2)
```

## Robotics

```{r robotics}
fanuc <- ggTS("6954 JT Equity", title = "FANUC")
keyence <- ggTS("6861 JT Equity", title = "Keyence")
grid.arrange(fanuc)
```

## US Banks

```{r us_banks}
jpm <- ggTS("JPM US Equity", "JP Morgan")
wf <- ggTS("WFC US Equity", "Wells Fargo")
bac <- ggTS("BAC US Equity", "Bank of America")
citi <- ggTS("C US Equity", "Citigroup")
gs <- ggTS("GS US Equity", "Goldman Sachs")
ms <- ggTS("MS US Equity", "Morgan Stanley")
grid.arrange(jpm, wf, bac, citi, gs, ms, nrow = 2)
```

## Asset Managers

```{r asset_mgmt}
blk <- ggTS("BLK US Equity", title = "BlackRock")
bony <- ggTS("BK US Equity", title = "Bank of New York")
ss <- ggTS("STT US Equity", title = "State Street")
nt <- ggTS("NTRS US Equity", title = "Northern Trust")
grid.arrange(blk, bony, ss, nt, nrow = 2)
```

## Private equity

```{r private_equity}
bs <- ggTS("BX US Equity", title = "BlackStone Group")
kkr <- ggTS("KKR US Equity", title = "KKR & Co LP")
apo <- ggTS("APO US Equity", title = "Apollo Global")
cg <- ggTS("CG US Equity", title = "Carlyle Group")
oak <- ggTS("OAK US Equity", title = "Oaktree Capital")
iii <- ggTS("III LN Equity", title = "3i")
grid.arrange(bs, kkr, apo, cg, oak, iii, nrow = 2)
```

## Cryptocurrencies

```{r crypto}
bitcoin <- ggTS("XBTUSD BGN Curncy", title = "Bitcoin")
ripple <- ggTS("XRPUSD BGN Curncy", title = "Ripple")
ethereum <- ggTS("XETUSD BGN Curncy", title = "Ethereum")
litecoin  <- ggTS("XLCUSD BGN Curncy", title = "Litecoin")
grid.arrange(bitcoin, ripple, ethereum, litecoin, nrow = 2)
```

## Asia indices
```{r asia_indices}
nikkei <- ggTS("NKY Index", title = "Nikkei")
hang_seng <- ggTS("HSI Index", title = "Hang Seng")
kospi <- ggTS("KOSPI Index", title = "KOSPI")
sti <- ggTS("STI Index", title = "STI")
grid.arrange(nikkei, hang_seng, kospi, sti, nrow = 2)
```

## Chinese stocks
```{r chinese_stocks}
hsbc <- ggTS("5 HK Equity", title = "HSBC")
c_merc <- ggTS("144 HK Equity", title = "China Merchants")
ccb <- ggTS("939 HK Equity", title = "China Construction Bank")
c_mob <- ggTS("941 HK Equity", title = "China Mobile")
icbc <- ggTS("1398 HK Equity", title = "ICBC")
boc <- ggTS("3988 HK Equity", title = "Bank of China")
grid.arrange(hsbc, c_merc, ccb, c_mob, icbc, boc, nrow = 2)
```

## BAT+
```{r bat}
baba <- ggTS("BABA US Equity", title = "Alibaba")
baidu <- ggTS("BIDU US Equity", title = "Baidu")
tencent <- ggTS("TCEHY US Equity", title = "Tencent")
bzun <- ggTS("BZUN US Equity", title = "Baozun")
grid.arrange(baba, baidu, tencent, bzun, nrow = 2)
```

## Singapore stocks
```{r sgp_stocks}
capland <- ggTS("CAPL SP Equity", title = "Capitaland")
genting <- ggTS("GENS SP Equity", title = "Genting")
grid.arrange(capland, genting)
```
