---
title: "EZ econs chart pack"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
source("C:\\Users\\ylim\\Documents\\R projects\\tidymas\\R\\convenience.R")
```

#UK

## UK Growth
```{r uk_gdp}
uk_qtr_rgdp_yoy <- getMB("gbnaac00072")["2008/9999"] %>%  q_yoy()  %>% ggXTS(title = "UK Real Quarterly GDP YoY") + hline(0)
# uk_qtr_ngdp_yoy <- getMB("gbnaac00052")["2008/9999"] %>% q_yoy() %>% ggXTS(title = "UK Nominal Quarterly GDP YoY") + hline(0)
uk_ann_rgdp_yoy <- getMB("gbnaac00072")["2008/9999"] %>% apply.yearly(sum) %>% y_yoy() %>% ggXTS(title = "UK Real Annual GDP YoY") + hline(0) + geom_point()
# uk_ann_ngdp_yoy <- getMB("gbnaac00052")["2008/9999"] %>%  apply.yearly(sum) %>% y_yoy() %>% ggXTS(title = "UK Nominal Annual GDP YoY") + hline(0)
grid.arrange(uk_qtr_rgdp_yoy, uk_ann_rgdp_yoy, nrow=2)
# grid.arrange(uk_qtr_rgdp_yoy, uk_qtr_ngdp_yoy, uk_ann_rgdp_yoy, uk_ann_ngdp_yoy, nrow = 2)
```

## UK growth contributors
```{r gdp_growth_comp}

```


## UK Inflation
```{r uk_inf}
uk_cpi_yoy <- getMB("gbpric00011") %>% m_yoy %>% ggXTS("UK CPI YoY") + hline(2)
uk_rpi_yoy <- getMB("ons_czbh_mm23_m") %>% ggXTS("UK RPI YoY") + hline(0)
uk_gdpdf_yoy <- getMB("gbnaac22382") %>% q_yoy() %>% ggXTS("UK CPI deflator YoY") + hline(0)
#uk_cpi_mom <- getMB("gbpric00011") %>% m_mom %>% ggXTS("UK CPI MoM") 
grid.arrange(uk_cpi_yoy, uk_rpi_yoy, uk_gdpdf_yoy, nrow = 2)
```

## UK PMIs
```{r uk_lead}
uk_comp_pmi <- getMB("markit_pmigbcomob")["2008/9999"] %>% 
  ggXTS(title = "UK Composite PMI") + hline(50)
uk_manu_pmi <- getMB("markit_pmigbmanpm")["2008/9999"] %>% 
  ggXTS(title = "UK Manufacturing PMI") + hline(50)
uk_cons_pmi <- getMB("markit_pmigbconob")["2008/9999"] %>% 
  ggXTS(title = "UK Construction PMI") + hline(50) 
uk_svcs_pmi <- getMB("markit_pmigbserob")["2008/9999"] %>% 
  ggXTS(title = "UK Services PMI") + hline(50)
grid.arrange(uk_comp_pmi, uk_manu_pmi, uk_cons_pmi, uk_svcs_pmi, ncol = 2)
```

# UK Consumers

## Consumption
```{r uk_consumption, results='asis'}
uk_gfk <- getMB("gbsurv0515")["2008/9999"] %>% ggXTS(title = "GfK Consumer Survey") + hline(0)
uk_new_car_registrations <- getMB("gbsmmt0001")["2008/9999"] %>% m_yoy() %>% ggXTS(title = "New car registrations") + hline(0)
uk_retail_sales <- getMB("gbtrad1001") %>%  ggXTS("BRC Retail Sales, All Cateogories, %YoY")
grid.arrange(uk_gfk, uk_new_car_registrations, uk_retail_sales, nrow = 2)
```

## UK Labour Market
```{r uk_labour, results = "asis"}
uk_employment_rate <- getMB("gblama03431") %>%  ggXTS(title = "Employment rate") 
uk_unemployment_rate <- getMB("gblama1207") %>% ggXTS("Unemployment rate")
uk_awe <- getMB("gblama03032") %>%  q_yoy %>% ggXTS(title = "Average Weekly Wages")
uk_unfilled_services<- getMB("gblama04491") %>% m_yoy() %>% ggXTS("Unfilled vacancies in all services jobs") + hline(0)
grid.arrange(uk_employment_rate, uk_unemployment_rate, uk_awe, uk_unfilled_services, nrow = 2)
```

## UK Labour Market 2

```{r uk_labour2}
grid.arrange(
  getMB("gblama00371") %>% m_yoy() %>% ggXTS("Actual hours worked") + hline(0),
  getMB("gblama03022") %>% m_yoy() %>% ggXTS("Output per hour, constant prices, %YoY") + hline(0),
  getMB("gbnaac08882") %>%  ggXTS("Household savings ratio"),
  getMB("gbbank6176") %>%  ggXTS("Debt-to-Income Ratio for Households"),
  nrow = 2
)
```

## UK Labour Market 3

```{r uk_labour 3}
uk_awe_yoy <- getMB("gbinea00931") %>% ggXTS("Average Weekly Earnings, Whole Economy %YoY") + hline(0)
uk_awe_3mmma_yoy <- getMB("gbinea00941") %>% ggXTS("Average Weekly Earnings, Whole Economy 3MMA %YoY") + hline(0)
grid.arrange(uk_awe_yoy, uk_awe_3mmma_yoy)
```


## UK Housing
```{r uk_housing}
uk_nw_yoy <- getMB("gbcons0207")["2008/9999"] %>% m_yoy() %>% ggXTS(title = "Nationwide Price Index") + hline(0)
uk_halifax_yoy <- getBBG("UKHBSAMM Index") %>% ggXTS(title = "UK Markit/Halifax House Prices All UK MoM SA") + hline(0)
uk_halifax_3m_yoy <- getBBG("UKHB3MYR Index") %>% ggXTS(title = "UK Markit/Halifax House Prices 3mth YoY SA") 
grid.arrange(uk_nw_yoy, uk_halifax_yoy, uk_halifax_3m_yoy, nrow = 2)

```

## Investments

## Govt

## Exports

## Imports

# Eurozone

## Headlines
```{r ez_headlines}
ez_real_qtr_gdp <- getMB("eunaac2903") %>% q_yoy() %>% ggXTS(title = "Eurozone Real Quarterly GDP  %YoY") + hline(0)
ez_core_inf_yoy <- getMB("eupric0151") %>% m_yoy() %>% ggXTS(title = "EZ Core Inflation")
ez_unemp <- getMB("eulama3600") %>% ggXTS(title = "EZ Unemployment Rate")
grid.arrange(ez_core_inf_yoy, ez_unemp)
```

## EZ Growth
```{r ez_growth}
ez_real_qtr_gdp <- getMB("eunaac2903") %>% q_yoy() %>% ggXTS(title = "Eurozone Real Quarterly GDP SA %YoY") + hline(0)
ez_real_ann_gdp <- getMB("eunaac2903") %>% apply.yearly(sum) %>% y_yoy() %>% ggXTS(title = "Eurozone Real Annual GDP SA %YoY") + 
                    hline(0) + geom_point()
grid.arrange(ez_real_qtr_gdp, ez_real_ann_gdp)
```

## EZ inflation
```{r ez_inf}
ez_core_inf_yoy <- getMB("eupric0151") %>% m_yoy() %>% ggXTS(title = "EZ Core Inflation")
ez_hl_inf_yoy <- getMB("eupric0001") %>% m_yoy() %>% ggXTS(title = "EZ Headline Inflation")
grid.arrange(ez_core_inf_yoy, ez_hl_inf_yoy, nrow = 2)
```


## EZ PMIs
```{r ez_pmis}
ez_comp_pmi <- getMB("markit_pmiezcomob")["2008/9999"] %>% 
  ggXTS(title = "EZ Composite PMI") + hline(50)
ez_manu_pmi <- getMB("markit_pmiezmanpm")["2008/9999"] %>% 
  ggXTS(title = "EZ Manufacturing PMI") + hline(50)
ez_cons_pmi <- getMB("markit_pmiezconob")["2008/9999"] %>% 
  ggXTS(title = "EZ Construction PMI") + hline(50)
ez_svcs_pmi <- getMB("markit_pmiezserob")["2008/9999"] %>% 
  ggXTS(title = "EZ Services PMI") + hline(50)
grid.arrange(ez_comp_pmi, ez_manu_pmi, ez_cons_pmi, ez_svcs_pmi, ncol = 2)
```

# Germany

## German Growth
```{r de_growth}
de_real_qtr_gdp <- getMB("denaac0152") %>% q_yoy() %>% ggXTS(title = "Germany Real Quarterly GDP %YoY") + hline(0)
de_real_ann_gdp <- getMB("denaac0152") %>% apply.yearly(sum) %>% y_yoy() %>% ggXTS(title = "Germany Real Annual GDP %YoY") + 
                    hline(0) + geom_point()
grid.arrange(de_real_qtr_gdp, de_real_ann_gdp)
```

## German Inflation

```{r de_inf}
de_inf_yoy <- getMB("depric1962") %>% m_yoy() %>% ggXTS(title = "German Harmonised Inflation %YoY")
grid.arrange(de_inf_yoy)
```

## German PMI
```{r de_pmi}
de_comp_pmi <- getMB("markit_pmidecomob")["2008/9999"] %>% 
  ggXTS(title = "Germany Composite PMI") + hline(50)
de_manu_pmi <- getMB("markit_pmidemanpm")["2008/9999"] %>% 
  ggXTS(title = "Germany Manufacturing PMI") + hline(50)
de_cons_pmi <- getMB("markit_pmideconob")["2008/9999"] %>% 
  ggXTS(title = "Germany Construction PMI") + hline(50)
de_svcs_pmi <- getMB("markit_pmideserob")["2008/9999"] %>% 
  ggXTS(title = "Germany Services PMI") + hline(50)
grid.arrange(de_comp_pmi, de_manu_pmi, de_cons_pmi, de_svcs_pmi, ncol = 2)
```

# France

## France Growth
```{r fr_growth}
fr_real_qtr_gdp <- getMB("frnaac0284") %>% q_yoy() %>% ggXTS(title = "France Real Quarterly GDP  %YoY") + hline(0)
fr_real_ann_gdp <- getMB("frnaac0284") %>% apply.yearly(sum) %>% y_yoy() %>% ggXTS(title = "France Real Quarterly GDP  %YoY") + 
                    hline(0) + geom_point()
grid.arrange(fr_real_qtr_gdp, fr_real_ann_gdp)
```

## France Inflation

```{r fr_inf}
fr_inf_yoy <- getMB("frpric0611") %>% m_yoy() %>% ggXTS(title = "France Harmonised Inflation %YoY")
grid.arrange(fr_inf_yoy)
```


## France PMI
```{r fr_pmi}
fr_comp_pmi <- getMB("markit_pmifrcomob")["2008/9999"] %>% 
  ggXTS(title = "France Composite PMI") + hline(50)
fr_manu_pmi <- getMB("markit_pmifrmanpm")["2008/9999"] %>% 
  ggXTS(title = "France Manufacturing PMI") + hline(50)
fr_cons_pmi <- getMB("markit_pmifrconob")["2008/9999"] %>% 
  ggXTS(title = "France Construction PMI") + hline(50)
fr_svcs_pmi <- getMB("markit_pmifrserob")["2008/9999"] %>% 
  ggXTS(title = "France Services PMI") + hline(50)
grid.arrange(fr_comp_pmi, fr_manu_pmi, fr_cons_pmi, fr_svcs_pmi, ncol = 2)
```

# Italy

## Italy Growth
```{r it_growth}
it_real_qtr_gdp <- getMB("itnaac0466") %>% q_yoy() %>% ggXTS(title = "Italy Real Quarterly GDP  %YoY") + hline(0)
it_real_ann_gdp <- getMB("itnaac0466") %>% apply.yearly(sum) %>%  q_yoy() %>% ggXTS(title = "Italy Real Quarterly GDP  %YoY") + 
                    hline(0) + geom_point()
grid.arrange(it_real_qtr_gdp, it_real_ann_gdp)
```

## Italy Inflation

```{r it_inf}
it_inf_yoy <- getMB("itpric0286") %>% m_yoy() %>% ggXTS(title = "Italy Harmonised Inflation %YoY")
grid.arrange(it_inf_yoy)
```

## Italy PMI
```{r it_pmi}
it_comp_pmi <- getMB("markit_pmiitcomob")["2008/9999"] %>% 
  ggXTS(title = "Italy Composite PMI") + hline(50)
it_manu_pmi <- getMB("markit_pmiitmanpm")["2008/9999"] %>% 
  ggXTS(title = "Italy Manufacturing PMI") + hline(50)
it_cons_pmi <- getMB("markit_pmiitconob")["2008/9999"] %>% 
  ggXTS(title = "Italy Construction PMI") + hline(50)
it_svcs_pmi <- getMB("markit_pmiitserob")["2008/9999"] %>% 
  ggXTS(title = "Italy Services PMI") + hline(50)
grid.arrange(it_comp_pmi, it_manu_pmi, it_cons_pmi, it_svcs_pmi, ncol = 2)
```

# Spain

## Spain Growth
```{r es_growth}
es_real_qtr_gdp <- getMB("esnaac0097") %>% q_yoy() %>% ggXTS(title = "Spain Real Quarterly GDP %YoY") + hline(0)
es_real_ann_gdp <- getMB("esnaac0097") %>% apply.yearly(sum) %>% y_yoy() %>% ggXTS(title = "Spain Real Annual GDP %YoY") + 
                    hline(0) + geom_point()
grid.arrange(es_real_qtr_gdp)
```

## Spain Inflation

```{r es_inf}
es_inf_yoy <- getMB("espric4357") %>% m_yoy() %>% ggXTS(title = "Spain Harmonised Inflation %YoY")
grid.arrange(es_inf_yoy)
```

## Spain PMI
```{r es_pmi}
es_comp_pmi <- getMB("markit_pmiescomob")["2008/9999"] %>% 
  ggXTS(title = "Spain Composite PMI") + hline(50)
es_manu_pmi <- getMB("markit_pmiesmanpm")["2008/9999"] %>% 
  ggXTS(title = "Spain Manufacturing PMI") + hline(50)
es_cons_pmi <- blank_chart() #Spain has no construction PMI
es_svcs_pmi <- getMB("markit_pmiesserob")["2008/9999"] %>% 
  ggXTS(title = "Spain Services PMI") + hline(50)
grid.arrange(es_comp_pmi, es_manu_pmi, es_cons_pmi, es_svcs_pmi, ncol = 2)
```

# Netherlands

## Netherlands Growth
```{r nl_growth}
nl_real_qtr_gdp <- getMB("nlnaac1067") %>% q_yoy() %>% ggXTS(title = "Netherlands Real Quarterly GDP %YoY") + hline(0)
nl_real_ann_gdp <- getMB("nlnaac1067") %>% apply.yearly(sum) %>% q_yoy() %>% ggXTS(title = "Netherlands Real Annual GDP %YoY") + 
                    hline(0) + geom_point()
grid.arrange(nl_real_qtr_gdp, nl_real_ann_gdp)
```

## Netherlands Inflation

```{r nl_inf}
nl_inf_yoy <- getMB("nlpric1838") %>% m_yoy() %>% ggXTS(title = "Netherlands Harmonised Inflation %YoY")
grid.arrange(nl_inf_yoy)
```

## Netherlands PMI
```{r nl_pmi}
nl_manu_pmi <- getMB("markit_pminlmanpm")["2008/9999"] %>% 
  ggXTS(title = "Netherlands Manufacturing PMI") + hline(50)
grid.arrange(nl_manu_pmi)
```

# Belgium

## Belgium Growth
```{r be_growth}
be_real_qtr_gdp <- getMB("benaac0274") %>% q_yoy() %>% ggXTS(title = "Netherlands Real Quarterly GDP  %YoY") + hline(0)
be_real_ann_gdp <- getMB("benaac0274") %>% apply.yearly(sum) %>% q_yoy() %>% ggXTS(title = "Netherlands Real Annual GDP %YoY") + 
                    hline(0) + geom_point()
grid.arrange(be_real_qtr_gdp, be_real_ann_gdp)
```

## Belgium Inflation

```{r be_inf}
be_inf_yoy <- getMB("bepric1354") %>% m_yoy() %>% ggXTS(title = "Belgium Harmonised Inflation %YoY")
grid.arrange(be_inf_yoy)
```

# Ireland

## Ireland Growth
```{r ie_growth}
ie_real_qtr_gdp <- getMB("ienaac2033") %>% q_yoy() %>% ggXTS(title = "Ireland Real Quarterly GDP  %YoY") + hline(0)
ie_real_ann_gdp <- getMB("ienaac2033") %>% apply.yearly(sum) %>% q_yoy() %>% ggXTS(title = "Ireland Real Annual GDP %YoY") + 
                    hline(0) + geom_point()
grid.arrange(ie_real_qtr_gdp, ie_real_ann_gdp)
```

## Ireland Inflation

```{r ie_inf}
ie_inf_yoy <- getMB("iepric0231") %>% m_yoy() %>% ggXTS(title = "Ireland Harmonised Inflation %YoY")
grid.arrange(ie_inf_yoy)
```

## Ireland PMI
```{r ie_pmi}
ie_comp_pmi <- getMB("markit_pmiiecomob")["2008/9999"] %>% 
  ggXTS(title = "Ireland Composite PMI") + hline(50)
ie_manu_pmi <- getMB("markit_pmiiemanpm")["2008/9999"] %>% 
  ggXTS(title = "Ireland Manufacturing PMI") + hline(50)
ie_cons_pmi <- getMB("markit_pmiieconob")["2008/9999"] %>% 
ggXTS(title = "Ireland Construction PMI") + hline(50)
ie_svcs_pmi <- getMB("markit_pmiieserob")["2008/9999"] %>% 
  ggXTS(title = "Ireland Services PMI") + hline(50)
grid.arrange(ie_comp_pmi, ie_manu_pmi, ie_cons_pmi, ie_svcs_pmi, ncol = 2)
```
